---
title: "Analysis. Experiment 2: five game objects."
format: html
---

```{r}
#| warning: false
#| message: false
library(tidyverse)

library(cmdstanr)
library(glue)
library(loo)
library(progress)

source("common.R")
```

## Comparing models via LOO

```{r}
loo_files <- fs::dir_ls("Loos/exp2-five-objects", glob = "*loo_exp2_*.RDS", type = "file")
model_names <- 
  loo_files |>
  fs::path_file() |>
  fs::path_ext_remove() |>
  stringr::str_remove("loo_exp2_")
loos <- purrr::map(loo_files, ~readRDS(.))
names(loos) <- model_names

model_comparison <- compute_loo_summary_df(loos)
model_comparison
```

## Getting draws for the selected model

```{r}
selected_model <- "[set-memory]_[obj-common]_[color-perset]"
draws_filename <- glue::glue("Draws/exp2-five-objects/draws_exp2_{selected_model}.RDS")

if (fs::file_exists(draws_filename)) {
  draws <- readRDS(draws_filename)
} else {
  stop("No file with sampled draws. Please fit the model (execute the chunk below) or contact authors for sampled draws.")
}
```

Emergency sampling if draws file is missing, disabled by default. Please note that the sampling could take at least a few hours.
```{r eval=FALSE}
stan_data <- readRDS("Data/exp2-five-objects/exp2-standata.RDS")

model <- cmdstan_model(glue::glue("Stan/exp2-five-objects/{selected_model}.stan"))

fit <- model$sample(data = data_for_stan, chains = 4, parallel_chains = future::availableCores())

draws <- fit$draws(format = "df") |> 
         as_tibble() |>
         select(-starts_with("log_lik"))
```


Loading posterior log-Likelihood. This is required to (re)compute LOO values for various subsets of trials but assumes that all sampled log likelihood values are stored in *LogLik* folder.
```{r}
#|eval: false
log_lik <- purrr::map(model_names, ~readRDS(glue("LogLik/exp2-five-objects/loglik_exp2_{.}.RDS")), progress = TRUE)
names(log_lik) <- model_names
```

Extract predictions for log(RT) for posterior predictions
```{r}
# extract predictions for log(RT)
predicted_logRT <-
  draws |>
  select(starts_with("logMu["))
```

## Import data and compute repetitions

```{r}
results <- 
  readRDS("Data/exp2-five-objects/exp2.RDS") |>
  
  # compute repetition counts per block
  group_by(participant.code, block) |>
  mutate(RepetitionObject = compute_repetitions(target),
         RepetitionColor = compute_repetitions(target_color),
         RepetitionSet = compute_repetitions(TrialAttentionSet)) |>
  ungroup()
```


Adding log Likelihood index depending on the first fitted trial
```{r}
data_for_stan <- readRDS("Data/exp2-five-objects/exp2-standata.RDS")
results$iloglik <- NA
ill <- 1
for(irow in 1:nrow(results)) {
  if (results$trial[irow] >= data_for_stan$FITTING_START_TRIAL) {
    results$iloglik[irow] <- ill
    ill <- ill + 1
  }
}
```


## Repetition priming: real vs. ideal observers

```{r}
Rpredict <- NULL # NULL (all) for final
Rsample <- 2000  # 2000 for final
```

### Repetition of both object and set

```{r}
object_and_set_repetition_filter <- function(df) {
  filter(df, RepetitionObject <= 3, RepetitionObject <= RepetitionSet, trial >= data_for_stan$FITTING_START_TRIAL)
}
```

Individual participants
```{r}
#|eval: false
avg_prediction_object_and_set <- compute_average_predicted_repetition("Object", object_and_set_repetition_filter, "participant", R=Rpredict)
avg_bootstrap_object_and_set <- sample_average_repetition("Object", object_and_set_repetition_filter, "participant", R=Rsample)

plot_repetition("Repetition of object and set",
                "Object",
                avg_prediction_object_and_set,
                avg_bootstrap_object_and_set,
                level = "participant")
```


Group averages
```{r}
if (fs::file_exists("Averages/object-and-set-exp2-posterior.RDS")) {
  avg_prediction_object_and_set_per_group <- readRDS("Averages/object-and-set-exp2-posterior.RDS")
} else {
  avg_prediction_object_and_set_per_group <- compute_average_predicted_repetition("Object", object_and_set_repetition_filter, "group", R=Rpredict)
  saveRDS(avg_prediction_object_and_set_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/object-and-set-exp2-posterior.RDS")
}

if (fs::file_exists("Averages/object-and-set-exp2-bootstrap.RDS")) {
  avg_bootstrap_object_and_set_per_group <- readRDS("Averages/object-and-set-exp2-bootstrap.RDS")
} else {
  avg_bootstrap_object_and_set_per_group <- sample_average_repetition("Object", object_and_set_repetition_filter, "group", R=Rsample)
  saveRDS(avg_bootstrap_object_and_set_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/object-and-set-exp2-bootstrap.RDS")
}

plot_repetition("Repetition of object and set",
                "Object",
                avg_prediction_object_and_set_per_group,
                avg_bootstrap_object_and_set_per_group,
                level = "group")
```

```{r}
if (fs::file_exists("Loos/exp2-five-objects/loo_object_and_set.RDS")) {
  loo_object_and_set <- readRDS("Loos/exp2-five-objects/loo_object_and_set.RDS")  
} else {
  loo_object_and_set <- loo_using_filter(results, log_lik, object_and_set_repetition_filter)
  saveRDS(loo_object_and_set, "Loos/exp2-five-objects/loo_object_and_set.RDS")
}

if (fs::file_exists("Loos/exp2-five-objects/loo_object_and_set_table.RDS")) {
  loo_object_and_set_table <- readRDS("Loos/exp2-five-objects/loo_object_and_set_table.RDS")
} else {
  loo_object_and_set_table <- compute_loo_summary_df(loo_object_and_set)
  saveRDS(loo_object_and_set_table, "Loos/exp2-five-objects/loo_object_and_set_table.RDS")
}
loo_object_and_set_table
```

### Object repeats, set changes

```{r}
object_not_set_repetition_filter <- function(df) {
  filter(df, RepetitionObject <= 3, RepetitionSet == 0, trial >= data_for_stan$FITTING_START_TRIAL)
}
```

Individual participants

```{r}
#|eval: false
avg_prediction_object_not_set <- compute_average_predicted_repetition("Object", object_not_set_repetition_filter, "participant", R=Rpredict)
avg_bootstrap_object_not_set <- sample_average_repetition("Object", object_not_set_repetition_filter, "participant", R=Rsample)

plot_repetition("Repetition of object not set",
                "Object",
                avg_prediction_object_not_set,
                avg_bootstrap_object_not_set,
                level = "participant")
```

Group averages
```{r}
if (fs::file_exists("Averages/object-not-set-exp2-posterior.RDS")) {
  avg_prediction_object_not_set_per_group <- readRDS("Averages/object-not-set-exp2-posterior.RDS")
} else {
  avg_prediction_object_not_set_per_group <- compute_average_predicted_repetition("Object", object_not_set_repetition_filter, "group", R=Rpredict)
  saveRDS(avg_prediction_object_not_set_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/object-not-set-exp2-posterior.RDS")
}

if (fs::file_exists("Averages/object-not-set-exp2-bootstrap.RDS")) {
  avg_bootstrap_object_not_set_per_group <- readRDS("Averages/object-not-set-exp2-bootstrap.RDS")
} else {
  avg_bootstrap_object_not_set_per_group <- sample_average_repetition("Object", object_not_set_repetition_filter, "group", R=Rsample)
  saveRDS(avg_bootstrap_object_not_set_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/object-not-set-exp2-bootstrap.RDS")
}

plot_repetition("Repetition of object not set",
                "Object",
                avg_prediction_object_not_set_per_group,
                avg_bootstrap_object_not_set_per_group,
                level = "group")
```

```{r}
if (fs::file_exists("Loos/exp2-five-objects/loo_object_not_set.RDS")) {
  loo_object_not_set <- readRDS("Loos/exp2-five-objects/loo_object_not_set.RDS")  
} else {
  loo_object_not_set <- loo_using_filter(results, log_lik, object_not_set_repetition_filter)
  saveRDS(loo_object_not_set, "Loos/exp2-five-objects/loo_object_not_set.RDS")
}

if (fs::file_exists("Loos/exp2-five-objects/loo_object_not_set_table.RDS")) {
  loo_object_not_set_table <- readRDS("Loos/exp2-five-objects/loo_object_not_set_table.RDS")
} else {
  loo_object_not_set_table <- compute_loo_summary_df(loo_object_not_set)
  saveRDS(loo_object_not_set_table, "Loos/exp2-five-objects/loo_object_not_set_table.RDS")
}

loo_object_not_set_table
```

### Object changes, set repeats

```{r}
set_not_object_repetition_filter <- function(df) {
  filter(df, RepetitionObject == 0, RepetitionSet <= 3, trial >= data_for_stan$FITTING_START_TRIAL)
}
```

Individual participants

```{r}
#|eval: false
avg_prediction_set_not_object <- compute_average_predicted_repetition("Set", set_not_object_repetition_filter, "participant", R=Rpredict)
avg_bootstrap_set_not_object <- sample_average_repetition("Set", set_not_object_repetition_filter, "participant", R=Rsample)

plot_repetition("Repetition of set not object",
                "Set",
                avg_prediction_set_not_object,
                avg_bootstrap_set_not_object,
                level = "participant")
```

Group averages
```{r}
if (fs::file_exists("Averages/set-not-object-exp2-posterior.RDS")) {
  avg_prediction_set_not_object_per_group <- readRDS("Averages/set-not-object-exp2-posterior.RDS")
} else {
  avg_prediction_set_not_object_per_group <- compute_average_predicted_repetition("Set", set_not_object_repetition_filter, "group", R=Rpredict)
  saveRDS(avg_prediction_set_not_object_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/set-not-object-exp2-posterior.RDS")
}

if (fs::file_exists("Averages/set-not-object-exp2-bootstrap.RDS")) {
  avg_bootstrap_set_not_object_per_group <- readRDS("Averages/set-not-object-exp2-bootstrap.RDS")
} else {
  avg_bootstrap_set_not_object_per_group <- sample_average_repetition("Set", set_not_object_repetition_filter, "group", R=Rsample)
  saveRDS(avg_bootstrap_set_not_object_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/set-not-object-exp2-bootstrap.RDS")
}

plot_repetition("Repetition of set not object",
                "Set",
                avg_prediction_set_not_object_per_group,
                avg_bootstrap_set_not_object_per_group,
                level = "group")
```

```{r}
if (fs::file_exists("Loos/exp2-five-objects/loo_set_not_object.RDS")) {
  loo_set_not_object <- readRDS("Loos/exp2-five-objects/loo_set_not_object.RDS")
} else {
  loo_set_not_object <- loo_using_filter(results, log_lik, set_not_object_repetition_filter)
  saveRDS(loo_set_not_object, "Loos/exp2-five-objects/loo_set_not_object.RDS")
}

if (fs::file_exists("Loos/exp2-five-objects/loo_set_not_object_table.RDS")) {
  loo_set_not_object_table <- readRDS("Loos/exp2-five-objects/loo_set_not_object_table.RDS")
} else {
  loo_set_not_object_table <- compute_loo_summary_df(loo_set_not_object)
  saveRDS(loo_set_not_object_table, "Loos/exp2-five-objects/loo_set_not_object_table.RDS")
}

loo_set_not_object_table
```

### Object changes, color and set repeat

```{r}
color_and_set_not_object_repetition_filter <- function(df) {
  filter(df, RepetitionObject == 0, RepetitionColor <= 3, RepetitionColor <= RepetitionSet, trial >= data_for_stan$FITTING_START_TRIAL)
}
```

Individual participants

```{r}
#|eval: false
avg_prediction_set_not_object <- compute_average_predicted_repetition("Set", set_not_object_repetition_filter, "participant", R=Rpredict)
avg_bootstrap_set_not_object <- sample_average_repetition("Set", set_not_object_repetition_filter, "participant", R=Rsample)

plot_repetition("Repetition of set not object",
                "Set",
                avg_prediction_set_not_object,
                avg_bootstrap_set_not_object,
                level = "participant")
```

Group averages
```{r}
if (fs::file_exists("Averages/color-and-set-not-object-exp2-posterior.RDS")) {
  avg_prediction_color_and_set_not_object_per_group <- readRDS("Averages/color-and-set-not-object-exp2-posterior.RDS")
} else {
  avg_prediction_color_and_set_not_object_per_group <- compute_average_predicted_repetition("Color", color_and_set_not_object_repetition_filter, "group", R=Rpredict)
  saveRDS(avg_prediction_color_and_set_not_object_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/color-and-set-not-object-exp2-posterior.RDS")
}

if (fs::file_exists("Averages/color-and-set-not-object-exp2-bootstrap.RDS")) {
  avg_bootstrap_color_and_set_not_object_per_group <- readRDS("Averages/color-and-set-not-object-exp2-bootstrap.RDS")
} else {
  avg_bootstrap_color_and_set_not_object_per_group <- sample_average_repetition("Color", color_and_set_not_object_repetition_filter, "group", R=Rsample)
  saveRDS(avg_bootstrap_color_and_set_not_object_per_group |> add_column(Experiment = "Experiment 2"),
          "Averages/color-and-set-not-object-exp2-bootstrap.RDS")
}

plot_repetition("Repetition of color and set, not object",
                "Color",
                avg_prediction_color_and_set_not_object_per_group,
                avg_bootstrap_color_and_set_not_object_per_group,
                level = "group")
```

```{r}
if (fs::file_exists("Loos/exp2-five-objects/loo_color_and_set_not_object.RDS")) {
  loo_color_and_set_not_object <- readRDS("Loos/exp2-five-objects/loo_color_and_set_not_object.RDS")
} else {
  loo_color_and_set_not_object <- loo_using_filter(results, log_lik, color_and_set_not_object_repetition_filter)
  saveRDS(loo_color_and_set_not_object, "Loos/exp2-five-objects/loo_color_and_set_not_object.RDS")
}

if (fs::file_exists("Loos/exp2-five-objects/loo_color_and_set_not_object_table.RDS")) {
  loo_color_and_set_not_object_table <- readRDS("Loos/exp2-five-objects/loo_color_and_set_not_object_table.RDS")
} else {
  loo_color_and_set_not_object_table <- compute_loo_summary_df(loo_color_and_set_not_object)
  saveRDS(loo_color_and_set_not_object_table, "Loos/exp2-five-objects/loo_color_and_set_not_object_table.RDS")
}

loo_color_and_set_not_object_table
```


